---
title: "Next Gen Data Science"
format: html
jupyter: .venv/bin/python
---

# Data Connection
## ODBC with R
```{r}
library(tidyverse)
```

Connect to data in Snowflake

```{r}
con <- DBI::dbConnect(
    odbc::snowflake(),
    warehouse = "DEFAULT_WH"
)
```

## Snowflake Python Connector
Interactive Snowflake queries from Python
```{python}
import snowflake.connector
conn = snowflake.connector.connect()
cur = conn.cursor()
cur.execute('select * from AIR_QUALITY_DATA_UNITED_STATES.PUBLIC.AIR_QUALITY limit 10')
df = cur.fetch_pandas_all()
df
```

Grab all data from the table locally for the time being

```{python}
cur.execute("SELECT * FROM AIR_QUALITY_DATA_UNITED_STATES.PUBLIC.AIR_QUALITY")
df = cur.fetch_pandas_all()
```

## SQLAlchemy
Can SQLAlchemy use the OAuth configuration? Documentation suggests username and password are required parameters

```{python}
import os
from sqlalchemy import create_engine, text

account = os.getenv("SNOWFLAKE_ACCOUNT")
engine = create_engine(f"snowflake://{account}/?connection_name=workbench")

with engine.connect() as conn:
    print(conn.execute(text("SELECT current_version()")).fetchall())
```

Now let's connect to an actual dataset via SQLAlchemy

```{python}
# This works as expected
with engine.connect() as conn:
    print(conn.execute(text("SELECT * FROM AIR_QUALITY_DATA_UNITED_STATES.PUBLIC.AIR_QUALITY LIMIT 10")).fetchall())
```

Now to create a specific connection in the engine itself
```{python}
from sqlalchemy import create_engine, text
from snowflake.sqlalchemy import URL
engine = create_engine(URL(
    account = account,
    connection_name = "workbench",
    database = "AIR_QUALITY_DATA_UNITED_STATES",
    schema = "PUBLIC",
    warehouse = "DEFAULT_WH",
    role = "DEVELOPER"
))

with engine.connect() as conn:
    print(conn.execute(text("SELECT * FROM AIR_QUALITY LIMIT 10")).fetchall())
```


# Gen AI
## Elmer

```{r}
library(ellmer)
```

## Chatlas
Anthropic
```{python}
from chatlas import ChatAnthropic
chat = ChatAnthropic()
```

```{python}
chat.console()
```

Snowflake

```{python}
from chatlas import ChatSnowflake
chat = ChatSnowflake(
    model = "claude-3-5-sonnet"
)
```

```{python}
chat.console()
```


